%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer, Motion Algorithm Team} % Job title
    {Roboe Technologies} % Organization
    {Seoul, South Korea} % Location
    {Mar. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Trajectory Generator for Virtual Controllers}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
            \setlength{\parskip}{0pt}
            \renewcommand{\labelitemi}{\bullet}
            \item {Implemented motion planning algorithms for moveL and moveJ paths using C++}
          \end{itemize}
        }
        \item {\textbf{Motion Task Framework Development}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
            \setlength{\parskip}{0pt}
            \renewcommand{\labelitemi}{\bullet}
            \item {Reconstructed Behavior Tree into a graph-based architecture for better flexibility}
            \item {Solved Python GIL limitations using Ray-based multiprocessing}
            \item {Implemented shared process communication between main and child processes for efficient data exchange}
          \end{itemize}
        }
        \item {\textbf{Predictive Collision Shield System}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
            \setlength{\parskip}{0pt}
            \renewcommand{\labelitemi}{\bullet}
            \item {Implemented a velocity-based Predictive Collision Shield using MoveIt2’s FCL collision detection module}
          \end{itemize}
        }
        \item {\textbf{Jamming detection system}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
            \setlength{\parskip}{0pt}
            \renewcommand{\labelitemi}{\bullet}
            \item {Developed an algorithm to detect conveyor jamming using robot geometric information.}
            \item {Optimized the PointCloud2 filtering algorithm to operate within 0.05 Hz.}
          \end{itemize}
        }
        \item {\textbf{Conveyor Workspace Optimization for Mobile Robots}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
            \item {Developed a workspace analysis framework for a conveyor-mounted mobile robot on reachability area.}
            \item {Constructed a system model and cost-function optimization to minimize uncovered workspace regions based on reachability data.}
          \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern, Autonomous Driving Software} % Job title
    {Gole Robotics} % Organization
    {Seoul, South Korea} % Location
    {Aug. 2023 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a serial communication library}
        \item {Selected and tested sensors for autonomous driving}
        \item {Built a ROS2-based Docker development environment}
        \item {\textit{Recipient of the CES Innovation Award Honoree (2024).}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Researched robot planning and control system for mobile robot and manipulator} % Job title
  {Undergraduate Researcher, RAISE Lab(Prof. Youngmoon Lee)} % Organization
  {Ansan, South Korea} % Location
  {Jan. 2023 - Feb. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Developed autonomous driving software architecture and ROS2-based development environment.}
      \item {Designed and implemented a serial communication library and conducted sensor evaluation for autonomous driving.}
      \item {Published two research papers at international and domestic conferences:}
      \begin{itemize}
        \item {\textbf{Chanyeok Choi, \underline{Jeonghan Kim}, Yunjae Nam, Youngmoon Lee}, \textit{Snapbot: Enabling Dynamic Human–Robot Interactions for Real-Time Computational Photography}, \textbf{ACM/IEEE HRI 2024}, Boulder, USA.}
        \item {\textbf{\underline{Jeonghan Kim}, Jongchan Park, Hayeon Lee, Suhwan Park, Yunjae Nam, Gihyeon Kwon, Woohyeon Jung, Youngmoon Lee}, \textit{Separable Integrated Drone–Mobile Robot System for Unmanned Patrol}, \textbf{ICROS 2023}, Samcheok, South Korea.}
      \end{itemize}
      \item {Recipient of the \textbf{ICROS 2023 Undergraduate Best Paper Award}.}
      % \item {Achieved 2\textsuperscript{nd} place in the \textbf{National Software Capstone Design Competition}.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
